Global SOC maps and emissions

### 2020-06-26 ResultNotebooks/results_SOCmaps.Rmd
update results

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data", extras="--keep-newer-files ")

@@

SoilCarbon[,,"naturalstate.crop"] <- SoilCarbon[,,"naturalstate.natveg"]
SOCStock        <- dimSums(dimSums(SoilCarbon[,,"state",pmatch=TRUE], dim=3.3)* Landuse, dim=3.2)
glo_SOCStock    <- dimSums(SOCStock, dim=1) 
glo_SOCEmission <- glo_SOCStock[,,"naturalstate"] - glo_SOCStock[,,"actualstate"]  
plot(getYears(glo_SOCEmission, as.integer = TRUE),glo_SOCEmission/1000, type="l", xlab="Time", ylab="Global SOC Debt in GtC")
plot(getYears(glo_SOCEmission, as.integer = TRUE),glo_SOCStock[,,"actualstate"])
lines(getYears(glo_SOCEmission, as.integer = TRUE),glo_SOCStock[,,"naturalstate"])
```

@@

library(RColorBrewer)
cols      <- colorRampPalette(brewer.pal(11, "RdYlGn"))(7)
cols_dens <- colorRampPalette(brewer.pal(11, "RdYlGn"))(30)[c(1:20, rep(c(21:30), each=10))]
outputdir <- "Output/Images"

png(paste0(outputdir,"CDens_2010.png"), width = 1280, height = 720, res = 108)
luplot::plotmap(cropland_dens[,"y2010",], legend_range = c(0,300), legend_colours = cols_dens , main="Soil Organic Carbon Stocks under Cropland")
dev.off()

# png(paste0(outputdir,"CShare_1965.png"),width = 1280, height = 720, res = 108)
# luplot::plotmap(cropland_share[,"y1965",], legend_range = c(0,2), legend_colours = cols, main="C_share on Cropland 1965")
# dev.off()

png(paste0(outputdir,"CShare_2010.png"), width = 1280, height = 720, res = 108)
luplot::plotmap(cropland_share[,"y2010",], legend_range = c(0,2), legend_colours = cols, main="Stock Change Factor on Cropland 2010")
dev.off()

# png(paste0(outputdir,"CIncrease_1965.png"),width = 1280, height = 720, res = 108)
# luplot::plotmap(cropland_increase[,"y1965",], legend_range = c(-80,80), legend_colours = cols, main="Absoulte C change on Cropland 1965")
# dev.off()

png(paste0(outputdir,"CIncrease_2010.png"),width = 1280, height = 720, res = 108)
luplot::plotmap(cropland_increase[,"y2010",], legend_range = c(-80,80), legend_colours = cols, legend_title = "tC/ha", main="Absoulte C change on Cropland 2010")
dev.off()

@@

par(mfrow = c(2, 2))

luplot::plotmap(cropland_dens[,"y2010",], legend_range = c(0,300), legend_colours = cols_dens , 
                main="SOC Stocks under Cropland")
plot(getYears(glo_SOCEmission, as.integer = TRUE),glo_SOCEmission/1000, type="l", xlab="Time",
     ylab="Global SOC Debt in GtC")
luplot::plotmap(cropland_share[,"y2010",], legend_range = c(0,2), legend_colours = cols)
luplot::plotmap(cropland_increase[,"y2010",], legend_range = c(-80,80), legend_colours = cols,
                legend_title = "tC/ha")

>>>>

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
#untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data", extras="--keep-newer-files ")

@@

SoilCarbon[,,"naturalstate.crop"] <- SoilCarbon[,,"naturalstate.natveg"]
SOCStock        <- dimSums(dimSums(SoilCarbon[,,"state",pmatch=TRUE], dim=3.3)* Landuse, dim=3.2)
glo_SOCStock    <- dimSums(SOCStock, dim=1) 
glo_SOCEmission <- (glo_SOCStock[,,"naturalstate"] - glo_SOCStock[,,"actualstate"])/1000
plot(getYears(glo_SOCEmission, as.integer = TRUE),glo_SOCEmission/1000, type="l", xlab="Time", ylab="Global SOC Debt in GtC")
plot(getYears(glo_SOCEmission, as.integer = TRUE),glo_SOCStock[,,"actualstate"])
lines(getYears(glo_SOCEmission, as.integer = TRUE),glo_SOCStock[,,"naturalstate"])

SOCemis <- ggplot() + geom_line(data= as.data.frame(glo_SOCEmission)[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = "Global cummulative SOC emission in GtC") +
  scale_x_discrete(breaks=seq(1965,2010,5)) +
  scale_y_continuous(limits=c(25,40), breaks=seq(25,40,5)) +
  theme(rect=element_blank())

@@

library("ggplot2")
theme_set(theme_bw())
library("sf")
library("rnaturalearth")
library("rnaturalearthdata")
library(RColorBrewer)

cols_dens <- colorRampPalette(brewer.pal(11, "RdYlBu"))(30)[c(1:20, rep(c(21:30), each=10))]

outputdir <- "Output/Images"

world         <- ne_countries(scale = "medium", returnclass = "sf")
magpie_coord  <- toolGetMapping("magpie_coord.rda", type="cell")
share2plot    <- merge(as.data.frame(cropland_share), data.frame(magpie_coord, Cell=c(1:59199)), by="Cell")
increase2plot <- merge(as.data.frame(cropland_increase), data.frame(magpie_coord, Cell=c(1:59199)), by="Cell")
density2plot  <- merge(as.data.frame(cropland_dens), data.frame(magpie_coord, Cell=c(1:59199)), by="Cell")
cols          <- colorRampPalette(brewer.pal(11, "RdYlBu"))(7)
world.robin   <- st_transform(world,"+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")

SOCshare <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(share2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(0,2), colours = cols, 
                      name = expression("ratio of cropland SOC to potential natural SOC"), 
                      breaks=c(0.3,0.6,0.9,1.1,1.4,1.7,2),
                      labels=c("0     0.3","  0.6", "  0.9","  1.1","  1.4","  1.7","> 2"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=10),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = T,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7))
          )

SOCincrease <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(increase2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(-100,100), colours = cols, 
                      name = expression("cropland SOC change in tons of carbon per hectar"), 
                      values=(c(-100,-50,-20,-10,10,20,50,100)+100)/200,
                      breaks=c(-50,-20,-10,10,20,50,100),
                      labels=c("> -100    -50", "  -20","  -10","  10","  20","  50"," > 100"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=10),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = T,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7))
          )

cols <- colorRampPalette(brewer.pal(9, "YlGn"))(8)[2:8]
display.brewer.pal(9, "YlGn")
display.brewer.pal(9, "RdYlGn")

SOCdensity <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(density2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(0,150), colours = cols, 
                      name = expression("cropland SOC in tons of carbon per hectar"), 
                      values=c(0,5,10,20,40,70,100,150)/150,
                      breaks=c(5,10,20,40,70,100,150),
                      labels=c("0     5","  10","  20","  40","  70","  100"," >150"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=10),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = T,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7))
          )

# png(paste0(outputdir,"CDens_2010.png"), width = 1280, height = 720, res = 108)
# luplot::plotmap2(cropland_dens[,"y2010",], legend_range = c(0,300), lowcol = cols[1], midcol = cols[4], highcol = cols[7], ncol=7, legend_discrete = TRUE)
# dev.off()
# 
# # png(paste0(outputdir,"CShare_1965.png"),width = 1280, height = 720, res = 108)
# # luplot::plotmap(cropland_share[,"y1965",], legend_range = c(0,2), legend_colours = cols, main="C_share on Cropland 1965")
# # dev.off()
# 
# png(paste0(outputdir,"CShare_2010.png"), width = 1280, height = 720, res = 108)
# luplot::plotmap(cropland_share[,"y2010",], legend_range = c(0,2), legend_colours = cols, main="Stock Change Factor on Cropland 2010")
# dev.off()
# 
# # png(paste0(outputdir,"CIncrease_1965.png"),width = 1280, height = 720, res = 108)
# # luplot::plotmap(cropland_increase[,"y1965",], legend_range = c(-80,80), legend_colours = cols, main="Absoulte C change on Cropland 1965")
# # dev.off()
# 
# png(paste0(outputdir,"CIncrease_2010.png"),width = 1280, height = 720, res = 108)
# luplot::plotmap(cropland_increase[,"y2010",], legend_range = c(-80,80), legend_colours = cols, legend_title = "tC/ha", main="Absoulte C change on Cropland 2010")
# dev.off()

@@

grid <- grid.arrange(SOCdensity, SOCemis, SOCincrease, SOCshare, ncol=2)
grid
ggsave(paste0(outputdir,"/4panelfigure.png"), plot=grid)
